---
title: "Exploratory info on Software Architectural Styles"
author: Roman Liskunov
date: 11.11.2020
output: html_document
---

[Software systems](#https://www.kaggle.com/qadeemkhan/dataset-of-software-architectural-styles) are composed of one or more software architectural styles. These styles define the usage patterns of a programmer in order to develop a complex project. These architectural styles are required to analyze for pattern similarity in the structure of multiple groups of projects. The researcher can apply different types of data mining algorithms to analyze the software projects through architectural styles used. The dataset is obtained from an online questionnaire delivered to the world 's best academic and software industry.

Load Libraries:
```{r, results='hide', message=FALSE}
library("dplyr")
library("plotrix")
```


Load Libraries and Data:
```{r, warning=FALSE}
csv <- read.csv('software.csv', header = TRUE)
summary(csv)
```

Rename Data:
```{r}
frame <- tibble(csv)
data <- frame %>%
  select(
    Timestamp,
    Your.Good.Name.,
    Organization.,
    Last.Degree.,
    Job.Experience..,
    X1..How.Many.Repository.Architectural.Styles.have.you.used.for.a.particular.project.,
    X2..How.Many.Client.Server.Styles.you.have.used.for.a.particular.project.,
    X3..How.Many.Abstract.Machine.Styles.you.have.used.for.a.particular.project.,
    X4..How.Many.Object.Oriented.Styles.you.have.used.for.a.particular.project.,
    X5..How.Many.Function.Oriented.Styles.you.have.used.for.a.particular.project.,
    X6..How.Many.Event.Driven.Styles.you.have.used.for.a.particular.project.,
    X7..How.Many.Layered.Styles.you.have.used.for.a.particular.project.,
    X8..How.Many..Pipes...Filters.Architectural.Styles..have.you.used.for.a.particular.project.,
    X9..How.Many..Data.centeric.Architectural.Styles.have.you.used.for.a.particular.project.,
    X10..How.Many..Blackboard..Architectural.Styles.have.you.used.for.a.particular.project.,
    X11..How.Many..Rule.Based.Architectural.Styles.have.you.used.for.a.particular.project.,
    X12..How.Many.Publish.Subscribe.Architectural.Styles.have.you.used.for.a.particular.project.,
    X13..How.Many..Asynchronous.Messaging.Architectural.Styles.have.you.used.for.a.particular.project.,
    X14..How.Many..Plug.ins.Architectural.Styles.have.you.used.for.a.particular.project.,
    X15..How.Many..Micro.kernel.Architectural.Styles.have.you.used.for.a.particular.project.,
    X16..How.Many..Peer.to.Peer.Architectural.Styles.have.you.used.for.a.particular.project.,
    X17..How.Many..Domain.Driven.Architectural.Styles.have.you.used.for.a.particular.project.,
    X18..How.Many..Shared.Nothing.Architectural.Styles.have.you.used.for.a.particular.project.
  ) %>%
  rename(
    time = Timestamp,
    name = Your.Good.Name.,
    organization = Organization.,
    degree = Last.Degree.,
    job = Job.Experience..,
    x1 = X1..How.Many.Repository.Architectural.Styles.have.you.used.for.a.particular.project.,
    x2 = X2..How.Many.Client.Server.Styles.you.have.used.for.a.particular.project.,
    x3 = X3..How.Many.Abstract.Machine.Styles.you.have.used.for.a.particular.project.,
    x4 = X4..How.Many.Object.Oriented.Styles.you.have.used.for.a.particular.project.,
    x5 = X5..How.Many.Function.Oriented.Styles.you.have.used.for.a.particular.project.,
    x6 = X6..How.Many.Event.Driven.Styles.you.have.used.for.a.particular.project.,
    x7 = X7..How.Many.Layered.Styles.you.have.used.for.a.particular.project.,
    x8 = X8..How.Many..Pipes...Filters.Architectural.Styles..have.you.used.for.a.particular.project.,
    x9 = X9..How.Many..Data.centeric.Architectural.Styles.have.you.used.for.a.particular.project.,
    x10 = X10..How.Many..Blackboard..Architectural.Styles.have.you.used.for.a.particular.project.,
    x11 = X11..How.Many..Rule.Based.Architectural.Styles.have.you.used.for.a.particular.project.,
    x12 = X12..How.Many.Publish.Subscribe.Architectural.Styles.have.you.used.for.a.particular.project.,
    x13 = X13..How.Many..Asynchronous.Messaging.Architectural.Styles.have.you.used.for.a.particular.project.,
    x14 = X14..How.Many..Plug.ins.Architectural.Styles.have.you.used.for.a.particular.project.,
    x15 = X15..How.Many..Micro.kernel.Architectural.Styles.have.you.used.for.a.particular.project.,
    x16 = X16..How.Many..Peer.to.Peer.Architectural.Styles.have.you.used.for.a.particular.project.,
    x17 = X17..How.Many..Domain.Driven.Architectural.Styles.have.you.used.for.a.particular.project.,
    x18 = X18..How.Many..Shared.Nothing.Architectural.Styles.have.you.used.for.a.particular.project.
  )
```

Exploratory Analysis on Job Experience:
```{r}
j <- data %>% count(job)
print(j)
pie3D(
  j$n,
  labels = j$job,
  explode = 0.1,
  main = "Pie Chart of Job.Experience"
)
```

Exploratory Analysis on Last Degree acquired:
```{r}
d <- data %>% count(degree)
print(d)
pie3D(
  d$n,
  labels = d$degree,
  explode = 0.1,
  main = "Pie Chart of Last.Degree"
)
```